---
title: "Data Envelopment Analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

	Formulate and perform DEA analysis under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH.

Facility 1
```{r}
library(lpSolveAPI)
dmu1 <- read.lp("DMU1.lp")
dmu1
solve(dmu1)
get.objective(dmu1)
get.variables(dmu1)
```

facility 2
```{r}
library(lpSolveAPI)
dmu2 <- read.lp("DMU2.lp")
dmu2
solve(dmu2)
get.objective(dmu2)
get.variables(dmu2)
```

facility-3
```{r}
library(lpSolveAPI)
dmu3 <- read.lp("DMU3.lp")
dmu3
solve(dmu3)
get.objective(dmu3)
get.variables(dmu3)
```

facility 4
```{r}
library(lpSolveAPI)
dmu4 <- read.lp("DMU4.lp")
dmu4
solve(dmu4)
get.objective(dmu4)
get.variables(dmu4)
```

facility 5
```{r}
library(lpSolveAPI)
dmu5 <- read.lp("DMU5.lp")
dmu5
solve(dmu5)
get.objective(dmu5)
get.variables(dmu5)
```

facility 6
```{r}
library(lpSolveAPI)
dmu6 <- read.lp("DMU6.lp")
dmu6
solve(dmu6)
get.objective(dmu6)
get.variables(dmu6)
```

Benchmarking
```{r}
library(Benchmarking)
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2.0,1.2,0.7),ncol=2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(y) <- c("reimbursed","privately paid")
colnames(x) <- c("staff","supplies")
x
y
```

DEA analysis
```{r}
DEA <- dea(x,y,RTS = "crs")            
DEA
DEA1 <- dea(x,y,RTS = "fdh")            
DEA1
DEA2 <- dea(x,y,RTS = "vrs")           
DEA2
DEA3 <- dea(x,y,RTS = "irs")            
DEA3
DEA4 <- dea(x,y,RTS = "drs")           
DEA4
DEA5 <- dea(x,y,RTS = "add")            
DEA5
DEA6 <- dea(x,y,RTS = "vrs+")  
DEA6
DEA7 <- dea(x,y,RTS = "irs2")
DEA7
DEA8 <- dea(x,y,RTS = "fdh+") 
DEA8
```

Finding peers
```{r}
peers(DEA)
peers(DEA1)
peers(DEA2)
peers(DEA3)
peers(DEA4)
peers(DEA5)
peers(DEA6)
peers(DEA7)
peers(DEA8)
```

Finding lambda
```{r}
lambda(DEA)
lambda(DEA1)
lambda(DEA2)
lambda(DEA3)
lambda(DEA4)
lambda(DEA5)
lambda(DEA6)
lambda(DEA7)
lambda(DEA8)
```
#	Compare and contrast the above results

->constant return to scale method results indicates that DMU 1,2,3,4 are efficient.
->DMU 4 is 0.9777 efficient and DMU 5 is 0.8675 efficient.
->Free Disposability Hull)—> All DMUs are efficient. VRS(variable returns to scale) —>DMU 1,2,3,4,5 are efficient and DMU 6 is 0.8963 efficient. IRS(Increasing return to scale)
–>DMU 1,2,3,4,5 are efficient and DMU 6 is 0.8963 efficient. DRS(decreasing retun to scale)
—>DMU 1,2,3,4 are efficient ,DMU 5 is 0.9775 efficient and DMU 6 is 0.8963 efficient. FRH/Add (Free replicability hull)
—> All DMUs are efficient
