---
title: "Weigelt Corporation"
---


If you have not yet installed the `lpSolveAPI`, use `install.packages` from the tools menu to do so. Or, just use the code below.

* Note that lines that start with # are comments. 
* At any point, use the Console to look for help about a particular function using ?. For example `?make.lp()` 
* To run a chunk, the executable code, select the chunk, and use the Run button above to run that chunk. There are also keyboard shortcuts you can use to run chunks.

```{r, eval=FALSE}
install.packages("lpSolveAPI")
```

Now, load the library
```{r}
library(lpSolveAPI)
```

***
Let us set up the WGC problem. Note that we had two decision variables, and three constraints.
In the first formulation, we will directly create the objective function and constraints
```{r}
# make an lp object with 0 constraints and 9 decision variables
lprec <- make.lp(nrow=0, ncol=9)

set.objfn(lprec, c(420, 360, 300, 420, 360, 300, 420, 360, 300))

lp.control(lprec,sense='max')

add.constraint(lprec, c(1, 1, 1,0,0,0,0,0,0), "<=", 750)
add.constraint(lprec, c(0,0,0,1, 1, 1,0,0,0), "<=", 900)
add.constraint(lprec, c(0,0,0,0,0,0,1, 1, 1), "<=", 450)
add.constraint(lprec, c(20,15,12,0,0,0,0,0,0), "<=", 13000)
add.constraint(lprec, c(0,0,0,20,15,12,0, 0, 0), "<=", 12000)
add.constraint(lprec, c(0,0,0,0,0,0,20, 15, 12), "<=", 5000)
add.constraint(lprec, c(1,0,0,1,0,0,1, 0, 0), "<=", 900)
add.constraint(lprec, c(0,1,0,0,1,0,0, 1, 0), "<=", 1200)
add.constraint(lprec, c(0,0,1,0,0,1,0, 0, 1), "<=", 750)


set.bounds(lprec, lower = c(0, 0), columns = c(1, 9)) #Not really needed


RowNames <- c("Cap1", "cap2", "cap3", "space1","space2","space3", "sale1","sale2","sale3")
ColNames <- c("L1", "M1","S1","L2", "M2","S2","L3", "M3","S3")
dimnames(lprec) <- list(RowNames, ColNames)

# Now, print out the model
lprec



```

We now solve the above LP problem
```{r}
solve(lprec)
```

The output above doesn't indicate that the answer is 0, but that there was a successful solution.
We now output the value of the objective function, and the variables
```{r}
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
```


***

We now read the lp formulation using an lp file. To read about about the lp format for files, you can read the documentation at http://lpsolve.sourceforge.net/5.5/lp-format.htm. 
